Appendix for: Deep Reinforcement Learning for Conservation Decisions

### 2020-12-11 manuscript/appendix.Rmd
hyperparameters

```{r setup, cache = FALSE, include = FALSE}
library(tidyverse)
library(patchwork)
library(reticulate)

@@

knitr::opts_chunk$set(echo=FALSE)
```

@@

## initialize the environment
env <- gym$make("fishing-v1")
```

```{r eval=!file.exists("cache/a2c.zip")}
# train an agent (model) on one of the environments:
## FIXME set tuned hyperparameters
td3 <- sb3$TD3('MlpPolicy', env, verbose=0L, seed = 42L) # Must use L for integers!
td3$learn(total_timesteps=300000L)
td3$save("cache/td3")
```

```{r}
# Simulate management under the trained agent
td3 <- sb3$A2C$load("cache/td3")
sims <- env$simulate(td3, reps = 500L)
policy <- env$policyfn(td3, reps = 50L)
```

@@

```{r fig1, fig.cap=""}
fig_sims / ( fig_policy + fig_reward)
```
Note that the A2C policy learns to shut down fishing entirely below a certain stock size, without any variation.  However, it keeps the fishery closed even once stock sizes are slightly higher than $B_{MSY}$.  Once it begins fishing, it slightly under-harvests for stock sizes a little over $B_{MSY}$, but tends to over-harvest for very large stock sizes (rarely ever realized, as fishing pressure is enough to keep it out of this range). Note also that the harvest varies across replicates, creating a fuzzy region in the policy function. Under such a policy, A2C maintains a stock size on average significantly above $B_{MSY}$, though also sees higher volatility particularly on the low side.  Note that due to the stochastic nature of the environment, any given replicate A2C may out-perform the optimal policy, though on average the optimal policy provides consistently better yields.

## Example of solving a problem that is difficult/impossible for conventional methods

two use cases to consider: 
  - model is known but too complex to solve by (approximate) dynamic programming etc, or non-markovian
  - model is unknown

model uncertainty/transfer learning? nonstationary dynamics?

## Example of an open problem without an RL solution

fire gym?

# Open issues

- wild west of AI?
- reproducibility
- AI ethics, transparency

# a vision going forward

- our public/open source environments and agents, leaderboard
- the need for collaborative/competitive development both to make better benchmark environments and better agents

>>>>

```{r knitr, include = FALSE}
knitr::opts_chunk$set(echo=FALSE)
```

```{r setup, cache = FALSE}
library(tidyverse)
library(patchwork)
library(reticulate)

@@

# force CPU-evaluation for reproducibility
Sys.setenv("CUDA_VISIBLE_DEVICES"="")

```

@@

## initialize the environment
env <- gym$make("fishing-v1", sigma = 0.1)
```

```{r eval=!file.exists("cache/a2c.zip")}
# train an agent (model) on one of the environments:

#Trial 15 finished with value: 7.6994757652282715 and parameters: 
hyper = list('gamma'= 0.995, 'lr'= 0.0001355522450968401, 'batch_size'= 128L, 
         'buffer_size'= 10000L, 'episodic'= FALSE, 'train_freq'= 128L, 
         'noise_type'= 'normal', 'noise_std'= 0.6656948079225263, 
         'net_arch'= 'big')
policy_kwargs = list(net_arch=c(400L, 300L)) # big

#non-episodic:
hyper['gradient_steps'] = hyper['train_freq']
hyper['n_episodes_rollout'] = -1
n_actions = env$action_space$shape[0]
hyper$action_noise = sb3$common$noise$NormalActionNoise(
        mean=np$zeros(n_actions),
        sigma= hyper[['noise_std']] * np$ones(n_actions)
        )

td3 = sb3$TD3('MlpPolicy', env,  verbose=0L, seed = 42L,
            gamma = hyper[['gamma']],
            learning_rate = hyper[['lr']],
            batch_size = hyper[['batch_size']],            
            buffer_size = hyper[['buffer_size']],
            action_noise = hyper[['action_noise']],
            train_freq = hyper[['train_freq']],
            gradient_steps = hyper[['train_freq']],
            n_episodes_rollout = hyper[['n_episodes_rollout']],
            policy_kwargs=policy_kwargs)

td3$learn(total_timesteps=300000L)
td3$save("cache/td3")
```

```{r}
# Simulate management under the trained agent
#td3 <- sb3$A2C$load("cache/td3") ## fixme, fails to load
sims <- env$simulate(td3, reps = 500L)
policy <- env$policyfn(td3, reps = 50L)
```

@@

```{r fig1, fig.cap=""}
fig_sims / ( fig_policy + fig_reward)
```
```{r}
```
